Clean data

### 2023-05-25 analysis/02_clean-data.Rmd
Updated indexed designs with an outside good indicator

# Create the arrays for the design, including a brand intercept.
index_X <- array(
  data = NA,
  dim = c(
    nrow(data),                   # Number of respondents.
    max(index_design$task),       # Number of choice tasks per respondent.
    (max(index_design$alt) + 1),  # Number of product alternatives per choice task.
    (ncol(index_design) - 3)      # Number of (estimable) attribute levels.
  )
)

@@

# Create the arrays for a design, including a brand intercept and interactions.
index_interactions_X <- array(
  data = NA,
  dim = c(
    nrow(data),                                # Number of respondents.
    max(index_interactions_design$task),       # Number of choice tasks per respondent.
    (max(index_interactions_design$alt) + 1),  # Number of product alternatives per choice task.
    (ncol(index_interactions_design) - 3)      # Number of (estimable) attribute levels.
  )
)

# Add the outside option coded as all zeros (org1 and former reference levels already included).
for (n in 1:dim(index_X)[1]) {
  # Filter for respondent n.
  index_X_n <- index_design %>% filter(version == data$version[n])
  interactions_X_n <- index_interactions_design %>% filter(version == data$version[n])
  for (s in 1:dim(index_X)[2]) {
    # Filter for task s.
    index_X_s <- index_X_n %>%
      filter(task == s) %>%
      select(org1:gov_rel3)
    interactions_X_s <- interactions_X_n %>%
      filter(task == s) %>%
      select(which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
    # Save modified design, including outside option.
    index_X[n, s,,] <- rbind(index_X_s, rep(0, ncol(index_X_s))) %>% as.matrix()
    index_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
  }
}
```

@@

# Create the arrays for the design, including a brand intercept.
flat_index_X <- array(
  data = NA,
  dim = c(
    nrow(data) * max(index_design$task), # Number of observations.
    (max(index_design$alt) + 1),         # Number of product alternatives per observation.
    (ncol(index_design) - 3)             # Number of (estimable) attribute levels.
  )
)

# Create the arrays for a design, including a brand intercept and interactions.
flat_index_interactions_X <- array(
  data = NA,
  dim = c(
    nrow(data) * max(index_interactions_design$task), # Number of respondents.
    (max(index_interactions_design$alt) + 1),         # Number of product alternatives per observation.
    (ncol(index_interactions_design) - 3)             # Number of (estimable) attribute levels.
  )
)

>>>>

# Create the arrays for the design, including a brand intercept and the outside option coded as an indicator.
index_X <- array(
  data = NA,
  dim = c(
    nrow(data),                   # Number of respondents.
    max(index_design$task),       # Number of choice tasks per respondent.
    (max(index_design$alt) + 1),  # Number of product alternatives per choice task.
    # (ncol(index_design) - 3)      # Number of (estimable) attribute levels.
    (ncol(index_design) - 3 + 1)  # Number of (estimable) attribute levels.
  )
)

@@

# Create the arrays for a design, including a brand intercept, 
# interactions, and the outside option coded as an indicator.
index_interactions_X <- array(
  data = NA,
  dim = c(
    nrow(data),                                # Number of respondents.
    max(index_interactions_design$task),       # Number of choice tasks per respondent.
    (max(index_interactions_design$alt) + 1),  # Number of product alternatives per choice task.
    # (ncol(index_interactions_design) - 3)      # Number of (estimable) attribute levels.
    (ncol(index_interactions_design) - 3 + 1)  # Number of (estimable) attribute levels.
  )
)

# Add the outside option coded as an indicator (org1 and former reference levels already included).
for (n in 1:dim(index_X)[1]) {
  # Filter for respondent n.
  index_X_n <- index_design %>% filter(version == data$version[n])
  interactions_X_n <- index_interactions_design %>% filter(version == data$version[n])
  for (s in 1:dim(index_X)[2]) {
    # Filter for task s.
    index_X_s <- index_X_n %>%
      filter(task == s) %>%
      mutate(out = 0) %>% # Add out column
      select(out, org1:gov_rel3)
    interactions_X_s <- interactions_X_n %>%
      filter(task == s) %>%
      mutate(out = 0) %>% # Add out column
      select(out, which(names(interactions_X_n) == "org1"):ncol(interactions_X_n))
    # Save modified design, including outside option.
    # index_X[n, s,,] <- rbind(index_X_s, rep(0, ncol(index_X_s))) %>% as.matrix()
    # index_interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
    index_X[n, s,,] <- rbind(index_X_s, c(1, rep(0, ncol(index_X_s) - 1))) %>% as.matrix()
    index_interactions_X[n, s,,] <- rbind(interactions_X_s, c(1, rep(0, ncol(interactions_X_s) - 1))) %>% 
      as.matrix()
  }
}
```

@@

# Create the arrays for the design, including a brand intercept and the outside option coded as an indicator.
flat_index_X <- array(
  data = NA,
  dim = c(
    nrow(data) * max(index_design$task), # Number of observations.
    (max(index_design$alt) + 1),         # Number of product alternatives per observation.
    # (ncol(index_design) - 3)             # Number of (estimable) attribute levels.
    (ncol(index_design) - 3 + 1)         # Number of (estimable) attribute levels.
  )
)

# Create the arrays for a design, including a brand intercept, 
# interactions, and the outside option coded as an indicator.
flat_index_interactions_X <- array(
  data = NA,
  dim = c(
    nrow(data) * max(index_interactions_design$task), # Number of respondents.
    (max(index_interactions_design$alt) + 1),         # Number of product alternatives per observation.
    # (ncol(index_interactions_design) - 3)             # Number of (estimable) attribute levels.
    (ncol(index_interactions_design) - 3 + 1)         # Number of (estimable) attribute levels.
  )
)
